\documentclass[12pt,a4paper]{article}
\usepackage[slovene]{babel}
\usepackage[cp1250]{inputenc}
\usepackage[usenames]{color}
\usepackage{pdfpages}
\usepackage{fullpage}
\usepackage{listings}
\begin{document}

\lstset{ %
language=C,                % choose the language of the code
basicstyle=\footnotesize,       % the size of the fonts that are used for the code
numbers=left,                   % where to put the line-numbers
numberstyle=\footnotesize,      % the size of the fonts that are used for the line-numbers
stepnumber=1,                   % the step between two line-numbers. If it's 1 each line will be numbered
numbersep=7pt,                  % how far the line-numbers are from the code
backgroundcolor=\color{white},  % choose the background color. You must add \usepackage{color}
showspaces=false,               % show spaces adding particular underscores
showstringspaces=false,         % underline spaces within strings
showtabs=false,                 % show tabs within strings adding particular underscores
frame=single,	                % adds a frame around the code
tabsize=2,	                % sets default tabsize to 2 spaces
captionpos=b,                   % sets the caption-position to bottom
breaklines=true,                % sets automatic line breaking
breakatwhitespace=false,        % sets if automatic breaks should only happen at whitespace
escapeinside={\%*}{*)}          % if you want to add a comment within your code
}

\begin{titlepage}
\begin{center}
{\Large Univerza v Ljubljani}\\
{\Large Fakulteta za raèunalništvo in informatiko}\\
\vspace{6 cm}
\textbf{{\LARGE Operacijski sistemi 2}}\\
\vspace{2 cm}
\textbf{{\LARGE Konèno poroèilo seminarske naloge MAIRM}}\\
\end{center}
\vspace{8.5 cm}

\begin{minipage}{\textwidth}
\begin{flushleft} \large
\textbf{Avtorja:}\\
Matej Jakop, 63070025\newline
Gregor Kališnik, VNESI VPISNO
\end{flushleft}
\end{minipage}\\
\vspace{1.0 cm}
\begin{center}
\textbf{Ljubljana, 25. maj 2010}
\end{center}
\end{titlepage}
\setcounter{page}{1}
\tableofcontents
\newpage
\section{Opis izbrane teme in problemskega podroèja}
\input{sections/opis_teme_problemskega_podrocja.tex}
\section{Izbrani cilji, zahteve ter omejitve}
\input{sections/izbrani_cilji_zahteve_omejitve.tex}
\section{Arhitektura rešitve}
\input{sections/arhitektura_resitve.tex}
\section{Izvedba rešitve in problemi pri tem}
\input{sections/izvedba_resitve_problemi.tex}
\section{Morebitno nadaljnje delo}
\input{sections/nadaljnje_delo.tex}
\section{Navodila za uporabo}
\input{sections/navodila_za_uporabo.tex}
\newpage
\addcontentsline{toc}{section}{Literatura} 
\begin{thebibliography}{1}
\bibitem{tasklets}
Tasklets.[Online].[Citirano: 17. januar 2010; 16:00]. Dostopno na spletnem naslovu: http://docs.blackfin.uclinux.org/doku.php?id=linux-kernel:tasklets.
\bibitem{tasklets2}
On using tasklets.[Online].[Citirano: 17. januar 2010; 16:22]. Dostopno na spletnem naslovu: http://www.cs.usfca.edu/~cruse/cs635/lesson17.ppt
\bibitem{dpc}
Deferred Procedure Call.[Online].[Citirano: 17. januar 2010; 17:00]. Dostopno na spletnem naslovu: http://en.wikipedia.org/wiki/Deferred\_Procedure\_Call
\bibitem{dpc_msdn}
Timer Objects and DPCs.[Online].[Citirano: 28. januar 2010; 16:00]. Dostopno na spletnem naslovu: http://msdn.microsoft.com/en-us/library/aa490171.aspx
\bibitem{freebsd_tasklet}
Scheduling a recurring task in a device drive.[Online].[Citirano: 28. januar 2010; 17:00]. Dostopno na spletnem naslovu:http://groups.google.si/group/mpc.lists.freebsd.hackers/browse\_thread/thread/fffc2a9181202627/6a6edd1ae2654fc3?hl=sl\&ie=UTF-8\&q=freebsd+tasklets\#6a6edd1ae2654fc3
\bibitem{lib_attack}Return-to-libc attack.[Online].[Citirano: 31. januar 2010; 13:00]. Dostopno na spletnem naslovu: http://en.wikipedia.org/wiki/Return-to-libc\_attack
\bibitem{buffer}
Writing buffer overflow exploits - a tutorial for beginners.[Online].[Citirano: 27. januar 2010; 18:00]. Dostopno na spletnem naslovu: http://mixter.void.ru/exploit.html
\bibitem{prosojnice}
Prosojnice s predavanj in zapiski
\bibitem{knjigaos}
Avi Silberschatz,A;Galvin,P in Gagne,G.(2005).Operating System Concepts.
\end{thebibliography}
\end{document}